### 2017-06-05 backmatter.tex
Own final read through
Final bits before submission
Corrections

\chapter*{List of Acronyms}
\addcontentsline{toc}{chapter}{List of Acronyms}
\begin{acronym}[CERN]
\acro{EM}[EM]{electromagnetic}
\acro{QFT}[QFT]{quantum field theory}
\acro{QCD}[QCD]{quantum chromodynamics}
\acro{QED}[QED]{quantum electrodynamics}
\acro{LEP}[LEP]{Large Electron-Positron}
\acro{VBF}[VBF]{vector boson fusion}
\acro{MC}[MC]{Monte Carlo}
\acro{CKM}[CKM]{Cabibbo-Kobayashi-Maskawa}
\acro{CMS}[CMS]{Compact Muon Solenoid}
\acro{LHC}[LHC]{Large Hadron Collider}
\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
\acro{PS}[PS]{Proton Synchrotron}
\acro{SPS}[SPS]{Super Proton Synchrotron}
\acro{PSB}[PSB]{Proton Synchrotron Booster}
\acro{LS1}[LS1]{Long Shutdown 1}
\acro{MSSM}[MSSM]{minimal supersymmetric standard model}
\acro{SM}[SM]{standard model}
\acro{SUSY}[SUSY]{supersymmetry}
\acro{2HDM}[2HDM]{two Higgs doublet model}
\acro{ECAL}[ECAL]{electromagnetic calorimeter}
\acro{HCAL}[HCAL]{hadron calorimeter}
\acro{TIB}[TIB]{Tracker Inner Barrel}
\acro{TID}[TID]{Tracker Inner Disk}
\acro{TOB}[TOB]{Tracker Outer Barrel}
\acro{TEC}[TEC]{Tracker EndCap}
\acro{EB}[EB]{ECAL Barrel}
\acro{EE}[EE]{ECAL Endcap}
\acro{HB}[HB]{Hadron Barrel Calorimeter}
\acro{HO}[HO]{Hadron Outer Calorimeter}
\acro{HE}[HE]{Hadron Endcap Calorimeter}
\acro{HF}[HF]{Hadron Forward Calorimeter}
\acro{BSM}[BSM]{beyond the standard model}
\acro{L1}[L1]{Level-1}
\acro{HLT}[HLT]{High-level trigger}
\acro{CSC}[CSC]{Cathode Strip Chamber}
\acro{DT}[DT]{Drift Tube chamber}
\acro{RPC}[RPC]{Resistive Plate Chamber}
\acro{DAQ}[DAQ]{Data Acquisition}
\acro{WLCG}[WLCG]{Worldwide LHC Computing Grid}
\acro{RF}[RF]{radio frequency}
\acro{PF}[PF]{particle flow}
\acro{BDT}[BDT]{boosted decision tree}
\acro{KF}[KF]{Kalman Filter}
\acro{CTF}[CTF]{Combinatorial Track Finder}
\acro{GSF}[GSF]{Gaussian Sum Filter}
%\acro{KF}[KF]{Kalman Filter}
\acro{DA}[DA]{Deterministic Annealing}
\acro{CHS}[CHS]{charged hadron subtraction}
\acro{CSV}[CSV]{Combined Secondary Vertex}
\acro{CL}[CL]{confidence level}
\acro{IVF}[IVF]{Inclusive Vertex Finder}
\acro{UE}[UE]{underlying event}
\acro{MPF}[MPF]{missing transverse energy projection fraction}
\end{acronym}

\appendix
\renewcommand{\chaptername}{Appendix}
\chapter{\texorpdfstring{Systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
\label{appendix:uncerts}
An overview of the systematic uncertainties that are applied in the MSSM \AHtotautau analysis (chapter \ref{chap:mssm})
are summarised in this appendix. The uncertainties are given in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
indicates that the uncertainty is correlated between categories but uncorrelated between
the different decay channels. For brevity the backgrounds are denoted with shorthand notations.
`ZTT' indicates the \Ztautau component. 'ZJ' is reserved for the \Zellell background
in which the tau is faked by a jet. The \Zellell background in which the tau is faked
by an electron or muon is indicated as 'ZL'. `W' indicates the \Wjets process. `TT' denotes
the \ttbar background, with  `TTT' and `TTJ'
indicating the \ttbar background with real hadronic taus and without real hadronic taus, respectively. 
The di-boson and single-top backgrounds are denoted `VV', with
`VVT' and `VVJ' indicating the di-boson plus single-top background with real hadronic taus
and without real hadronic taus, respectively. The QCD multijet background is denoted `QCD'.
\input{MSSM/UncOv}

>>>>

\chapter*{List of acronyms}
\addcontentsline{toc}{chapter}{List of acronyms}
\markboth{LIST OF ACRONYMS}{}
\begin{acronym}
\acro{2HDM}[2HDM]{two Higgs doublet model}
\acro{BDT}[BDT]{boosted decision tree}
\acro{BSM}[BSM]{beyond the standard model}
\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
\acro{CHS}[CHS]{charged hadron subtraction}
\acro{CKM}[CKM]{Cabibbo-Kobayashi-Maskawa}
\acro{CL}[CL]{confidence level}
\acro{CMS}[CMS]{Compact Muon Solenoid}
\acro{CSC}[CSC]{cathode strip chamber}
\acro{CSV}[CSV]{combined secondary vertex}
\acro{CTF}[CTF]{combinatorial track finder}
\acro{DA}[DA]{deterministic annealing}
\acro{DAQ}[DAQ]{data acquisition}
\acro{DT}[DT]{drift tube chamber}
\acro{EB}[EB]{ECAL barrel}
\acro{ECAL}[ECAL]{electromagnetic calorimeter}
\acro{EE}[EE]{ECAL endcap}
\acro{EM}[EM]{electromagnetic}
\acro{GSF}[GSF]{gaussian sum filter}
\acro{HB}[HB]{hadron barrel calorimeter}
\acro{HCAL}[HCAL]{hadron calorimeter}
\acro{HE}[HE]{hadron endcap calorimeter}
\acro{HF}[HF]{hadron forward calorimeter}
\acro{HLT}[HLT]{high-level trigger}
\acro{HO}[HO]{hadron outer calorimeter}
\acro{IVF}[IVF]{inclusive vertex finder}
\acro{KF}[KF]{Kalman filter}
\acro{L1}[L1]{level-1}
\acro{LEP}[LEP]{Large Electron-Positron}
\acro{LHC}[LHC]{Large Hadron Collider}
\acro{LS1}[LS1]{Long Shutdown 1}
\acro{MC}[MC]{Monte Carlo}
\acro{MPF}[MPF]{missing transverse energy projection fraction}
\acro{MSSM}[MSSM]{minimal supersymmetric standard model}
\acro{QCD}[QCD]{quantum chromodynamics}
\acro{PF}[PF]{particle flow}
\acro{PS}[PS]{Proton Synchrotron}
\acro{PSB}[PSB]{Proton Synchrotron Booster}
\acro{QED}[QED]{quantum electrodynamics}
\acro{QFT}[QFT]{quantum field theory}
\acro{RF}[RF]{radio frequency}
\acro{RPC}[RPC]{resistive plate chamber}
\acro{SM}[SM]{standard model}
\acro{SPS}[SPS]{Super Proton Synchrotron}
\acro{SUSY}[SUSY]{supersymmetry}
\acro{TEC}[TEC]{tracker endcap}
\acro{TIB}[TIB]{tracker inner barrel}
\acro{TID}[TID]{tracker inner disk}
\acro{TOB}[TOB]{tracker outer barrel}
\acro{UE}[UE]{underlying event}
\acro{VBF}[VBF]{vector boson fusion}
\acro{WLCG}[WLCG]{Worldwide LHC Computing Grid}
\end{acronym}

\appendix
\renewcommand{\chaptername}{Appendix}
\chapter{\texorpdfstring{Event yields in the \Htohhtobbtautau analysis}{Event yields in the H to hh to bbtautau analysis}}
\label{appendix:yields_bbtautau}
The numbers of observed and expected events in the \Htohhtobbtautau analysis \mbox{(chapter \ref{chap:hhh})}
are given in table \ref{tab:hhh_mt_yields} for the \mutau channel and in table \ref{tab:hhh_et_yields} for the \etau channel. The background
expectations are given after the fit to data has been performed. The uncertainties also correspond
to the values obtained after performing the fit to data, with the correlations between the different
systematic uncertainties taken into account. 
\input{Hhh/Hhhyields}

\chapter{\texorpdfstring{Systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
\label{appendix:uncerts}
An overview of the systematic uncertainties that are applied in the MSSM \AHtotautau analysis (chapter \ref{chap:mssm})
are summarised in this appendix. The uncertainties are given in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
indicates that the uncertainty is correlated between categories but uncorrelated between
the different decay channels. For brevity the backgrounds are denoted with shorthand notations.
`ZTT' indicates the \Ztautau component. 'ZJ' is reserved for the \Zellell background
in which the tau is faked by a jet. The \Zellell background in which the tau is faked
by an electron or muon is indicated as 'ZL'. `W' indicates the \Wjets process. `TT' denotes
the \ttbar background, with  `TTT' and `TTJ'
indicating the \ttbar background with real hadronic taus and without real hadronic taus, respectively. 
The di-boson and single-top backgrounds are denoted `VV', with
`VVT' and `VVJ' indicating the di-boson plus single-top background with real hadronic taus
and without real hadronic taus, respectively. The QCD multijet background is denoted `QCD'.
\input{MSSM/UncOv}

\chapter{\texorpdfstring{Event yields in the MSSM \AHtotautau analysis}{Event yields in the MSSM A/H to tautau analysis}}
\label{appendix:yields_mssm}
The numbers of observed and expected events in the MSSM \AHtotautau analysis \mbox{(chapter \ref{chap:mssm})}
are given in table \ref{tab:mssm_mt_yields} for the \mutau channel, in table \ref{tab:mssm_et_yields} for the 
\etau channel, in table \ref{tab:mssm_tt_yields} for the \tautau channel 
and in table \ref{tab:mssm_em_yields} for the \emu channel. The background
expectations are given after the fit to data has been performed. The uncertainties also correspond
to the values obtained after performing the fit to data, with the correlations between the different
systematic uncertainties taken into account. 
\input{MSSM/MSSMyields}

### 2017-06-05 frontmatter.tex
Corrections

% Declaration
\begin{declaration}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
Chapters \ref{chap:theory}--\ref{chap:objects} do not contain original work by myself, however they 
give information on the theoretical background, the CMS detector and the standard reconstruction algorithms
used within the CMS collaboration which underpin my own work described in later chapters.
The work for the \Htohhtobbtautau and \AHtotautau analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results of the \Htohhtobbtautau analysis I contributed to the data analysis of the \etau and \mutau
final states of the di-tau pair. I 
was responsible for the statistical inference of the analyses in the \etau, \mutau and \tautau final states
of the di-tau pair. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results of the \AHtotautau analysis
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for the \etau, \mutau and \tautau final states in the public result,
evaluation of systematic uncertainties in the \etau, \mutau, \tautau and \emu final states, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work on the combination of \AHtotautau analyses presented in chapter~\ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
\enlargethispage{2\baselineskip}

>>>>

% Declaration
\begin{declaration}
\small
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
Chapters \ref{chap:theory}--\ref{chap:objects} do not contain original work by myself, however they 
give information on the theoretical background, the CMS detector and the standard reconstruction algorithms
used within the CMS collaboration which underpin my own work described in later chapters.
The work for the \Htohhtobbtautau and \AHtotautau analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results of the \Htohhtobbtautau analysis I contributed to the data analysis of the \etau and \mutau
final states of the di-tau pair, with studies of alternative \ttbar background rejection methods and
other uses of the kinematic fit variable. These studies are not further discussed in this thesis. I 
was responsible for the statistical inference of the analyses in the \etau, \mutau and \tautau final states
of the di-tau pair. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results of the \AHtotautau analysis
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for the \etau, \mutau and \tautau final states in the public result,
evaluation of systematic uncertainties in the \etau, \mutau, \tautau and \emu final states, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work on the combination of \AHtotautau analyses presented in chapter~\ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
\enlargethispage{2\baselineskip}
